Turbulence in compact to giant HII regions

### 2022-02-18 strucfunc_paper.tex
Use new versions of strucfunc figures
and split them up into one figure per source

\begin{figure*}
  \centering
  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-A}
  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-A}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-B}
  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-B}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-C}
  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-C}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-D}
  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-D}
\end{figure*}

>>>>

\newcommand\sffig[1]{%
  \begin{tabular}{@{}ll@{}}
    (a)& (b)\\
    \includegraphics[width=0.45\linewidth]{Figures/sf-emcee-#1}
       &  \includegraphics[width=0.45\linewidth]{Figures/corner-emcee-#1}
  \end{tabular}%
}

\begin{figure*}
  \centering
  \sffig{OrionS}
  \caption{
    Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line from Orion core region.
  }
  \label{fig:strucfunc-fit-OrionS}
\end{figure*}
\begin{figure*}
  \centering
  \sffig{M8}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the Lagoon Nebula. 
  }
  \label{fig:strucfunc-fit-M8}
\end{figure*}
\begin{figure*}
  \centering
  \sffig{CarC}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the Carina Nebula. 
  }
  \label{fig:strucfunc-fit-CarC}
\end{figure*}

\begin{figure*}
  \centering
  \sffig{N346}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the NGC~346 nebula in the SMC. 
  }
  \label{fig:strucfunc-fit-N346}
\end{figure*}
\begin{figure*}
  \centering
  \sffig{Dor}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the 30~Doradus nebula in the LMC Nebula. 
  }
  \label{fig:strucfunc-fit-Dor}
\end{figure*}

\begin{figure*}
  \centering
  \sffig{HV}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the Hubble~V nebula.
  }
  \label{fig:strucfunc-fit-HV}
\end{figure*}
\begin{figure*}
  \centering
  \sffig{HX}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the Hubble~X nebula.
  }
  \label{fig:strucfunc-fit-HX}
\end{figure*}

\begin{figure*}
  \centering
  \sffig{N595}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the NGC~595 nebula.
  }
  \label{fig:strucfunc-fit-N595}
\end{figure*}
\begin{figure*}
  \centering
  \sffig{N604H}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the NGC~604 nebula.
  }
  \label{fig:strucfunc-fit-N604H}
\end{figure*}

\begin{figure*}
  \centering
  \sffig{OrionLH}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the extended Orion Nebula.
  }
  \label{fig:strucfunc-fit-OrionLH}
\end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-A}
%   \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-A}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-B}
%   \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-B}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-C}
%   \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-C}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-D}
%   \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-D}
% \end{figure*}
